\TheTitle

### 2017-07-14 paper/model.tex
editing model section

\section{Merge-Tree model}

\label{sec:mergetree}

The \mt model abstracts the DAG of the repository into a set of \mt{}s. Each \mt is rooted at a merge into the master
branch. The children of this tree are the commits and merges that are merged together into master by this merge. A \mt is build
recursively with every merge in the \mt merging a sub-\mt. Any merges that a commit must pass through to reach the
master branch become an inner node of the tree. 
Effectively, a \mt is a tree that
shows the path that commits follow in their way to the master branch of a repository.
The \mt{}s also help understand how commits were grouped together in order
to be integrated. In this model, not only has the DAG been inverted (and simplified), but
the entire notion of parent-child relationship has been reversed.

Please note that when we are referring to the
\mt, the parent is the next node toward the merge into the master
branch, or the root of the tree. When referring to the DAG, the parent
relationship is in the opposite direction, from the root toward the
branch-point. In addition to identifying the path that a commit took to
being merged, we are able to aggregate the commit metadata at merges as
we retain the parent-child and child-parent relationship for each event.

To illustrate this model we will use a small example:
assume the commits represented in
Figure~\ref{fig:repoEvents} show the sequence of events in a repository.
The sequence starts with the initiall commit in the master branch of the
master repository at time $t_0$. Repository event 1 is a commit, which
gets forked into a separate repository, \textit{Repo A}, where another
commit is made, event 2. Event 5 is a merge event, merging event 2, 3,
and 4 into \textit{Repo A}. Event 5 is branched from, event 6 happens in
the new branch, while event 7 is added simultaneously to the original
branch in \textit{Repo A}. Events 11 and 12 are both merge events,
merging changes made in \textit{Repo A} into the master branch of the
master repository.

As every repository is a first-class repository, including local copies
and forks, Git does not distinguish between forked repositories and
branches, and in neither case does it explicitly record where a commit
was made. In this case, commits are performed in various repositories
and branches. The DAG representation of these events is shown in
Figure~\ref{fig:repoDAG}.

 Notice that the DAG loses information about
the master branch and the repository that the master branch is part of.
The merge-tree view of this DAG is visible in Figure~\ref{fig:repoTree}.
Note that the direction of the edges of the DAG have been inverted,
instead of pointing from the child to the parent, it points from the
parent to its children, forming a path to the master branch. Also
note that the DAG has been simplified, showing only a single edge on the
path to master for any commit.

@@

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[auto, on grid, semithick, state/.style={circle, text=black}]
    \node[state, draw=chartblue] (1) {1};
    \node[state, draw=chartyellow, above right= of 1] (2) {2};
    \node[state, draw=chartmagenta, above right= 2cm and 1cm of 2] (3) {3};
    \node[state, draw=chartblue, right= 2cm of 1] (4) {4};
    \node[state, draw=chartyellow, above right=of 4] (5) {5};
    \node[state, draw=chartred, above right=of 5] (6) {6};
    \node[state, draw=chartyellow, right=of 5] (7) {7};
    \node[state, draw=chartmagenta, above right= 2cm and 1cm of 7](8) {8};
    \node[state, draw=chartyellow, right= 2cm of 7] (9) {9};
    \node[state, draw=chartyellow, right=of 9] (10) {10};
    \node[state, draw=chartblue, below right=of 9] (11) {11};
    \node[state, draw=chartblue, below right=of 10] (12) {12};

    \draw (12) edge[-stealth] (11) edge[chartyellow, -stealth] (10);
    \draw (11) edge[-stealth] (4) edge[chartyellow, -stealth] (9);
    \draw (10) edge[chartyellow, -stealth] (9);
    \draw (9) edge[chartmagenta, -stealth] (8) edge[chartred, -stealth] (6)
              edge[chartyellow, -stealth] (7);
    \draw (8) edge[chartmagenta, -stealth] (7);
    \draw (7) edge[chartyellow, -stealth] (5);
    \draw (6) edge[chartred, -stealth] (5);
    \draw (5) edge[chartmagenta, -stealth] (3) edge[chartyellow,-stealth] (2)
              edge[chartyellow, -stealth] (4);
    \draw (4) edge[-stealth] (1);
    \draw (3) edge[chartmagenta, -stealth] (2);
    \draw (2) edge[chartyellow, -stealth] (1);
  \end{tikzpicture}
  \caption{DAG representation of the commits represented in
    Figure~\ref{fig:repoEvents}. The DAG loses information about which
    repository the commit is performed in and through which merges it
    has passed on its way to the master branch. The DAG does not even
    distinguish the master branch from other branches.}
  \label{fig:repoDAG}
%\vspace{-3mm}
\end{figure}

@@

\subsection{Computing the merge-tree of the DAG of Linux}

Computing the merge-tree from a DAG for any repository may not be
possible; however, certain features of the development process of Linux
make it feasible to compute the merge-tree for the Linux repository.
First, the master branch of Linux is maintained by Linus Torvalds, and
only Linus has write access to it. We have verified this assertion in
previous research~\cite{German2015}. We have developed a heuristic that
is presented in Algorithm~\ref{fig:alg}. In short, the algorithm first
identifies the commits made directly to the master branch; whereafter it
recursively determines the shortest path (in terms of time), using the
DAG, from each commit to the master branch using the inverted DAG.

\dmg{I think you abbreviated this section too much. It will be helpful to describe the algorithm
at a very high level,as in the vissoft paper.}

\begin{algorithm}
        \caption{Computing the merge-tree of Linux Git's DAG}\label{fig:alg}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.}

@@

Merges that do not have conflicts provide information to verify this
heuristic. If a merge does not contain a conflict, it records a summary
of the commits that it merges. See Figure~\ref{fig:sampleMerge} for an
example. This summary contains a list of the first 20 non-merge commits
in the merge, including their one-line log description, the full logs of
the merge commits that merge this subset, and the total number of
non-merge commits in the merge.

@@

We used this information to evaluate the accuracy of the merge-tree
model extracted from the DAG\@. The method we followed started with the
extraction of the commit history up to July 20, 2016. We computed the
merge tree of every commit until then. Since Linus Torvalds mostly does
merging directly into master, we assumed that every merge by him is the
root of a merge-tree. As described above, the log of a merge-commit
usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds
using the command \mycode{log --merges --author='Torvalds} and compared
the number of commits according to the log with the number of commits in
the  merge-tree rooted in this commit. We also used the summaries of the
commits found in the merge (not necessarily all---see above) to make
sure those commits were in their corresponding merge tree. For example,
for the merge in Figure~\ref{fig:sampleMerge} we would expect that the
merge tree rooted at \mycode{8cbd84f} contains 24 commits, and the
one-line summaries corresponds to commits in that merge-tree. We also
inspected those with differences to make sure they were true errors.
The results can be summarized as follows:

@@

    The heuristic worked perfectly until Sept 4, 2007, the earliest date
    that it could be verified.  Before this date, and until Dec 12,
    2006, merges did not include a summary of the commits they included,
    hence making it impossible to verify; during this period, however,
    we correctly identified the merges by Linus into master.

@@

    Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
    presence of a \foxtrot commit (\mycode{c436688\ldots}),
    which confounded the true master branch of a repository.

>>>>

\section{Merge-Tree model}
\label{sec:mergetree}

The \mt model abstracts the DAG of the repository into a set of \mt{s}.
Each \mt is rooted at a merge into the master branch. The leaves of this
tree are the commits and the merges are the inner nodes. A \mt is built
recursively with every merge in the \mt merging a sub-\mt. Any merges
that a commit must pass through to reach the master branch become an
inner node of the tree. Effectively, a \mt is a tree that shows the path
that commits follow in their way to the master branch of a repository.
The \mt{s} also help understand how commits were grouped together in
order to be integrated. In this model, not only has the DAG been
inverted (and simplified), but the entire notion of parent-child
relationship has been reversed. Due to this property, the terminology
will be different depending on the model we are referring to; when we
are referring to the \mt, the parent is the next node toward the merge
into the master branch, or the root of the tree. When referring to the
DAG, the parent relationship is in the opposite direction, from the root
toward the branch-point. In addition to identifying the path that a
commit took to being merged, we are able to aggregate the commit
metadata at merges as we retain the parent-child and child-parent
relationship for each event and know which commits belong to the merge.

To illustrate this model we will use a small example: assume the commits
represented in Figure~\ref{fig:repoEvents} show the sequence of events
in a repository. The sequence starts with the initial commit in the
master branch of the master repository at time $t_0$. Repository event 1
is a commit, which gets forked into a separate repository, \textit{Repo
  A}, where another commit is made, event 2. Event 5 is a merge event,
merging event 2, 3, and 4 into \textit{Repo A}. Event 5 is branched
from, commit 6 happens in the new branch, while commit 7 is added
simultaneously to the original branch in \textit{Repo A}. Events 11 and
12 are both merge events, merging changes made in \textit{Repo A} into
the master branch of the master repository. As every repository is a
first-class repository, including local copies and forks, Git does not
distinguish between forked repositories and branches, and in neither
case does it explicitly record where a commit was made. In this case,
commits are performed in various repositories and branches. The DAG
representation of these events is shown in Figure~\ref{fig:repoDAG}.

Notice that the DAG loses information about the master branch and the
repository that the master branch is part of. The \mt view of
this DAG is visible in Figure~\ref{fig:repoTree}. Note that the
direction of the edges of the DAG have been inverted, instead of
pointing from the child to the parent, it points from the parent to its
children, forming a path to the master branch. Also note that the DAG
has been simplified, showing only a single edge on the path to master
for any commit.

@@

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[auto, on grid, semithick, state/.style={circle, text=black, black}]
    \node[state, black] (1) {1};
    \node[state, black, above right= of 1] (2) {2};
    \node[state, black, above right= 2cm and 1cm of 2] (3) {3};
    \node[state, black, right= 2cm of 1] (4) {4};
    \node[state, black, above right=of 4] (5) {5};
    \node[state, black, above right=of 5] (6) {6};
    \node[state, black, right=of 5] (7) {7};
    \node[state, black, above right= 2cm and 1cm of 7](8) {8};
    \node[state, black, right= 2cm of 7] (9) {9};
    \node[state, black, right=of 9] (10) {10};
    \node[state, black, below right=of 9] (11) {11};
    \node[state, black, below right=of 10] (12) {12};

    \draw (12) edge[-stealth] (11) edge[-stealth] (10);
    \draw (11) edge[-stealth] (4) edge[-stealth] (9);
    \draw (10) edge[-stealth] (9);
    \draw (9) edge[-stealth] (8) edge[-stealth] (6)
              edge[-stealth] (7);
    \draw (8) edge[-stealth] (7);
    \draw (7) edge[-stealth] (5);
    \draw (6) edge[-stealth] (5);
    \draw (5) edge[-stealth] (3) edge[-stealth] (2)
              edge[-stealth] (4);
    \draw (4) edge[-stealth] (1);
    \draw (3) edge[-stealth] (2);
    \draw (2) edge[-stealth] (1);
  \end{tikzpicture}
  \caption{DAG representation of the commits represented in
    Figure~\ref{fig:repoEvents}. The DAG loses information about which
    repository the commit is performed in and through which merges it
    has passed on its way to the master branch. The DAG does not even
    distinguish the master branch from other branches.}
  \label{fig:repoDAG}
%\vspace{-3mm}
\end{figure}

@@

\subsection{Computing the \mt of the DAG of Linux}

Computing the \mt from a DAG for any repository may not be
possible; however, certain features of the development process of Linux
make it feasible to compute the \mt for the Linux repository.
First, the master branch of Linux is maintained by Linus Torvalds, and
only Linus has write access to it. We have verified this assertion in
previous research~\cite{German2015}. We have developed a heuristic that
is presented in Algorithm~\ref{fig:alg}. In short, the algorithm first
identifies the commits made directly to the master branch, whereafter it
recursively determines the shortest path (in terms of time), using the
DAG, from each commit to the master branch using the inverted DAG.

\begin{algorithm}
        \caption{Computing the \mt of Linux Git's DAG}\label{fig:alg}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.}

@@

Merges that do not have conflicts provide information to verify this
heuristic. If a merge does not contain a conflict, it records a summary
of the commits that it merges. See Figure~\ref{fig:sampleMerge} for an
example. This summary contains a list of the first 20 non-merge commits
in the merge, including their one-line log description, and the total
number of non-merge commits in the merge.

@@

We used this information to evaluate the accuracy of the \mt model
extracted from the DAG\@. The method we followed started with the
extraction of the commit history up to July 20, 2016 form the Linux
repository. We computed the merge tree of every commit until that date.
Since Linus Torvalds mostly does merging directly into the master
branch, we assumed that every merge by Linus is the root of a \mt, later
detecting merges that do not merge into the master branch and removing
them from the set of root merges. As described above, the log of a
merge-commit usually contains the number of commits in the merge the
first 20 summaries of commits being merged. We extracted merges by Linus
Torvalds using the command \verb|git log --merges --author='Torvalds'|
and compared the number of commits according to the log with the number
of commits in the \mt rooted in this commit. We also used the summaries
of the commits found in the merge (not necessarily all---see above) to
make sure those commits were in their corresponding merge tree. For
example, for the merge in Figure~\ref{fig:sampleMerge} we would expect
that the merge tree rooted at \mycode{8cbd84f} contains 24 commits, and
the one-line summaries corresponds to commits in that \mt. We also
inspected those with differences to make sure they were true errors. The
results can be summarized as follows:

@@

    The heuristic worked perfectly until Sept 4, 2007, the earliest date
    that it could be verified.  Before this date, and until Dec 12,
    2006, merges did not include a summary of the commits they included,
    hence making it impossible to verify; during this period, however,
    we correctly identified the merges by Linus into the master branch.

@@

    Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
    presence of a \foxtrot commit (\mycode{c436688\ldots}),
    which confounded the true master branch.
